---
title: "Adding a Rcpp Function to Existing Class"
author: "Sean Wu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{addCpp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Add a Cpp function to existing R6 Class

in src/testMethods.cpp we define a function to use RcppArmadillo to do matrix multiplication on hte two matrices initialized in `testClass`. R/testClasses.R defines the R6 object as well as a function `addRcppMethod` that adds the cpp method `testMethodCpp` to the `R6ClassGenerator` object. 

Note that `addRcppMethod` actually defines the new method `testClass$testMethodCpp()` as a wrapper that passes the `private` environment down to the actual C++ code. This is because I have not been able to figure out so far how to directly "look up" to the enclosing R6 object from C++ and pull out the `private` enrivonment. Therefore we must use a wrapper to pass down that environment. 

### Future testing:

  * Can we directly grab the `public` environment from within the C++ code?
  * We should also test to make sure the environment is being passed as a reference and not being copied (maybe we can force this with `const Rcpp::Environment &testClassEnv`, also research into this option.)

The ultimate irony is that C++ is slower than R here. Always optimize intelligently! Compiled code is not always faster code.

```{r}
library(microbenchmark)
library(RcppQueues)
addRcppMethod()
xx = testClass$new(500)
microbenchmark(xx$testMethod(),xx$testMethodCpp())
```

